---
title: "TORs2 and 3"
output: beamer_presentation
slide_level: 3
theme: "Darmstadt"
logo: WHOI_NOAA_logo_smaller.png
date: "2024-02-02"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown

If you have trouble knitting this file, check out this page: https://stackoverflow.com/questions/67696286/error-generating-pdf-using-knitr-to-pdf-in-rstudio

* need to make the logo smaller on title and content slides (put it in the footer)

<!-- This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>. -->

<!-- When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. -->

## Outline

- 'Stock' parameters
- Fishery and index Parameters
- OM factors and simulated data examples
- EM models
- Beta standardization
- Analysis & Results
- Conclusions
- Future Work

## Stock parameters

- make some plots of maturity at age, weight at age, true deterministic SRR


## Fishery and index parameters

-- make some plots of fishery and index selectivity at age, q-index



## OM factors and simulated data examples

- make some plots to illustrate OM inputs and resulting simulated data generated

## EM models

- simple table listing EMs


## Couple of slides for Beta standardization

- greg's plots


## Analysis

\begin{enumerate}
  \item Convergence of the estimating models
  \item Model identifiability of an underlying stock recruitment model and/or an underlying relationship
   between environmental covariate 
  \item $\delta$AIC and model probability
  \item Assessment error (recruitment, spawning stock biomass, and Fbar)
  \item Bias of estimated parameters
  \item Mohn's $\rho$
  \item Projection performance relative to assumptions about the environmental covariate
\end{enumerate}







<!-- ```{r cars, echo = TRUE} -->
<!-- summary(cars) -->
<!-- ``` -->

## Slide with Plot

```{r pressure}
plot(pressure)
```

